Experiment 3 of 4

### 2018-08-11 experiments/D_exp_2/writeup/D_exp_2.Rmd
D_exp_2
only edits that made the code run.

```{r getData, echo=T}
# data.txt
rawdata <- read.table('preprocessing/data_processed.txt', sep=' ')
```

@@

```{r rtlmer, cache=TRUE}
rtlmer = lmerTest::lmer(data=rtdata,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
```

@@

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-3}
s1 <- subset(rtdata, subset=Selection=='Comparison')
s1lm <- lmerTest::lmer(data=s1, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s1lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-3}
s2 <- subset(rtdata, subset=Selection=='Matching')
s2lm <- lmerTest::lmer(data=s2, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s2lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

>>>>

```{r getData, echo=T}
# data_processed.txt has RT subset=RT>0 & RT<49871
rawdata <- read.table('preprocessing/data_processed.txt', sep=' ')
```

@@

```{r rtlmer, cache=TRUE}
dat_model <- rtdata
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtlmer = lmerTest::lmer(data=dat_model,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
```

@@

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-3}
dat_model <- subset(rtdata, subset=Selection=='Comparison')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
s1lm <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s1lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-3}
dat_model <- subset(rtdata, subset=Selection=='Matching')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
s2lm <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s2lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

### 2018-08-11 experiments/D_exp_2/writeup/preprocessing/preprocessing.Rmd
D_exp_2
only edits that made the code run.

@@

dat$Selection = ""
dat[dat$Condition %in% c(3,4), "Selection"] <- "Comparison"
dat[dat$Condition %in% c(1,2), "Selection"] <- "Matching"
dat$Condition <- NULL

dat$Selection <- as.factor(dat$Selection)

@@

# add preceding RT
my_rt <- dat$RT[-1]

dat$RTprev <- c(NA,dat$RT[1:nrow(dat)-1])

@@

dat$RT <- NULL
dat$RTprev <- NULL

@@

# This data set non-impossible trials and renamed/recomputed variables
# dat.out <- subset(dat, select=c(Subject, Trial, Item, c_Itm, Vagueness, c_Vag, Selection, c_Sel, Instruction, Order, Quantity, RT, RT_log, response_catResponse))
# write.table(dat.out, file="data_processed.txt")

dat <- subset(dat, select=c(Subject,Item,id,Trial,Vagueness,Selection, 
                             Order, Quantity, Instruction, nchar_instr, RT_raw, RT_log, RTprev_log, RTprev_raw, rt_instr, response_cat ))

>>>>

# The policy as of Aug 2018 is that:
# RT=0 is stripped, and one case with a very long time RT=49871 is stripped.

@@

# Create a factor coding for Selection
dat$Selection = ""
dat[dat$Condition %in% c(3,4), "Selection"] <- "Comparison"
dat[dat$Condition %in% c(1,2), "Selection"] <- "Matching"
dat$Condition <- NULL
dat$Selection <- as.factor(dat$Selection)

@@

# add preceding RT
dat$RTprev <- c(NA,dat$RT[1:nrow(dat)-1])

@@

dat$RTprev <- NULL

@@

dat <- subset(dat, 
              subset=RT>0 & RT<49871,
              select=c(Subject,Item,id,Trial,Vagueness,Selection, Order, Quantity, Instruction, nchar_instr, RT, RT_raw, RT_log, RTprev_log, RTprev_raw, rt_instr, response_cat ))
